MAESTROeX

### 2018-12-19 MAESTROeX_I/paper.tex
minor

\section{Test Problems}

\section{Performance and Scaling}

show OpenMP performance, maybe some comparisons with old Maestro?

@@

future stuff: rotation, SDC, high-order, GPUs

@@

>>>>

\section{Implementation and Performance}
show strong and/or weak scaling performance (with OpenMP threads/tiling), comparisons with old MAESTRO?

\section{Test Problems}
white dwarf convection runs at varying resolution

@@

future stuff
science: rotation, solar physics, MHD
algorithm: SDC, high-order
implementation: GPUs

@@

This work was supported by
